\documentclass[margin]{res}   
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}

\renewcommand{\headrule}{{ \hrule width 0.0cm height\headrulewidth \vskip-\headrulewidth}}

\thispagestyle{empty}
\addtolength{\voffset}{-1.0cm}
\addtolength{\hoffset}{-0.5cm}
\addtolength{\textwidth}{1.0cm}
\addtolength{\textheight}{0.5cm}
\addtolength{\headwidth}{1.0cm}
\addtolength{\headheight}{1cm}
\addtolength{\headsep}{0.5cm}


\lhead{}
\chead{} 
\rhead{\bfseries Hossein Falaki}
\lfoot{}
\cfoot{}
\rfoot{}
 
\font\attand=cmr7

\def\PS{{\tt P\small OST\tt S\small CRIPT}}
\def\ATT{{AT{\attand \&}T}}
\def\MF{{METAFONT}}
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\AmSTeX{{$\cal A\kern-.1667em\lower.5ex\hbox{$\cal M$}\kern-.125em
S$-\TeX}}

\renewcommand\namefont{\bf\huge}

\sectionskip=5mm

\resumewidth=5cm

\begin{document}

\name{Hossein Falaki}

\address{
1725 Liberty St., Apt 5\\
El Cerrito, CA 94530
}

\address{
Phone: 408-666-3793\\
Email: \href{mailto:falaki@gmail.com}{falaki@gmail.com}\\
Web: \href{http://www.falaki.net/}{www.falaki.net}
}


\begin{resume}

\begin{format}
\title{l}\employer{r}\\
\location{l}\dates{r}\\
\body\\
\end{format}

\section{\sc \large Summary}
I am an experienced software engineer and data scientist looking for new technical challenges at the intersection of computer science and statistics.

\title{\bf Software Engineer}
\employer {\href{http://www.databricks.com} {Databricks Inc.}}
\dates{\em 2013-present}
\location{San Francisco, CA}
\section{\sc \large Experience}
\begin{position}
I am one of the first software engineers at Databricks. I lead the end-to-end development of several product and open source features. Currently, I am responsible for R experience and machine learning ecosystem integration on the Databricks platform.
\end{position}

\vspace{-0.15cm}

\title{\bf Senior Data Scientist}
\employer {\href{http://www.apple.com} {Apple Inc.}}
\dates{\em 2012-2013}
\location{Cupertino, CA}
\begin{position}
Worked on modeling and improving accuracy and performance of Siri. My job required collaboration and data-driven communication with several other teams.
\end{position}

\vspace{-0.15cm}

\title{\bf  Research Assistant}
\employer {\href{http://www.ucla.edu/} {UCLA}}
\dates{\em 2008-2012}
\location{Los Angeles, CA}
\begin{position}
Worked with {\href{https://en.wikipedia.org/wiki/Deborah_Estrin} {Prof. Deborah Estrin}} on mobile sensing and mobile health projects at the Center for Embedded Networked Sensing of UCLA.
\end{position}

\vspace{-0.15cm}

\title{\bf  Research Intern}
\employer {\href{http://www.cisco.com/} {Cisco Systems}}
\dates{\em Summer 2010}
\location{San Jose, CA}
\begin{position}
Worked on vehicular mobile networking at {\href{http://www.cisco.com/web/about/ac50/ac207/crc_new/index.html} {Advanced Architecture and Research Group}}
.
\end{position}

\vspace{-0.15cm}

\title{\bf  Research Intern}
\employer {\href{http://research.microsoft.com/en-us/groups/nrg/} {Microsoft}}
\dates{\em Summer 2009}
\location{Redmond, WA}
\begin{position}
Worked at {\href{http://research.microsoft.com/en-us/groups/nrg/} {Microsoft Research}}
to understand how users interact with their smartphones.
\end{position}

\vspace{-0.15cm}

\title{\bf  Research Assistant}
\employer {\href{https://cs.uwaterloo.ca/} {University of Waterloo}}
\dates{\em 2006-2008}
\location{Waterloo, Ontario, Canada}
\begin{position}
Research assistant of {\href{https://en.wikipedia.org/wiki/Srinivasan_Keshav} {Prof. S. Keshav}} on the  {\href{https://en.wikipedia.org/wiki/KioskNet} {KioskNet}} project.
\end{position}


\title{\bf Ph.D. Computer Science}
\employer{}
\dates{2012}
\location{University of California, Los Angeles, CA}
\section{\sc \large Education}
\begin{position}
%\vspace{-0.6cm}
\end{position}

\vspace{-1.0cm}

\title{\bf  MMath. Computer Science}
\dates{2008}
\location{University of Waterloo, Ontario, Canada}
\begin{position}
\end{position}

\vspace{-1.0cm}

\title{\bf BS. Computer Engineering }
\employer{}
\dates{2006}
\location{Sharif University of Technology, Iran }
\begin{position}
\end{position}

\vspace{-1.0cm}

\title{\bf Diploma, Mathematics and Physics }
\employer{}
\dates{2002}
\location{National Organization for Exceptional Talents, Iran }
\begin{position}
\end{position}

\vspace{-0.5cm}

\section{\sc \large Graduate Coursework}
\begin{itemize}
\item {\bf University of Waterloo}: Advanced Algorithms, Game-Theoretic Methods, Internet Services and Performance, Computer and Communications Security, System Performance Evaluation
\item {\bf UCLA, Statistics}: Applied Probability, Theoretical Statistics, Advanced Modeling and Inference, Regression Analysis

\item {\bf UCLA, Computer Science}: Approximation Algorithms, Online Algorithms, Internet Architecture and Protocols, Advanced Topics in Internet Research, Queueing Systems Theory, Embedded Systems
\end{itemize}

\section{\sc \large Technical Skills}
\begin{itemize}
\item {\bf Programming Languages}: Scala, Java, R, Python
\item {\bf Machine Learning \& Statistical Analysis}:
Linear Modeling, Exploratory Data Analysis,\\ Statistical Data Visualization 
\item {\bf Performance Engineering}: Distributed Systems, JVM-based Applications, Service-oriented\\ Architecture, Web Applications
\end{itemize}

\section{\sc \large Publications}
Full list of citations are available on my \href{https://scholar.google.com/citations?user=wRw-e8EAAAAJ}{Google Scholars page}.
\begin{itemize}

\item Shivaram Venkataraman, Zongheng Yang, Davies Liu, Eric Liang, \emph{Hossein Falaki}, Xiangrui Meng, Reynold Xin, Ali Ghodsi, Michael Franklin, Ion Stoica, Matei Zaharia, 
{\bf ``SparkR: Scaling R Programs with Spark,``}
\emph{International Conference on Management of Data, 2016}

\item \emph{Hossein Falaki}, Ratul Mahajan, and Deborah Estrin, 
{\bf ``SystemSens: A Tool for Monitoring Usage in Smartphone Research
Deployments,''}
\emph{MobiArch, June 2011.}


\item \emph{Hossein Falaki}, Dimitrios Lymberopoulos, Ratul Mahajan, 
Srikanth Kandula, and Deborah Estrin, 
{\bf ``First Look at Traffic on Smartphones,''}
\emph{ACM IMC, November 2010.}


\item \emph{Hossein Falaki}, Ratul Mahajan, Srikanth Kandula,
Dimitrios Lymberopoulos, Ramesh Govindan, and Deborah Estrin, 
{\bf ``Diversity in Smartphone Usage,''}
\emph{ACM/USENIX MobiSys, June 2010.}


\item S. Guo, M. Derakhshani, \emph{M.H. Falaki}, U. Ismail, R. Luk, E.A. Oliver, S. Ur Rahman, A. Seth, M.A. Zaharia, and S. Keshav, 
{\bf ``Design and Implementation of the KioskNet System,''} 
\emph{Computer Networks, August 2010.}


\item \emph{Hossein Falaki}, Ramesh Govindan, and Deborah Estrin, 
{\bf ``Smart Screen Management on Mobile Phones,''}
\emph{Center for Embedded Network Sensing Technical Report, 
June 2009.}

\item \emph{Hossein Falaki}, and Sriniavasan Keshav, {\bf ``Trace-based
Analysis of Wi-Fi Scanning Strategies,''}\emph{ACM MCCR, January 2009.}

\item \emph{Hossein Falaki}, {\bf ``The Wi-Fi Roaming Game,''}
\emph{WINE, December 2007.}


\item S. Guo, \emph{M.H. Falaki}, E.A. Oliver, S. Ur Rahman, A. Seth, M.A. Zaharia, U. Ismail, and S. Keshav, 
{\bf ``Design and Implementation of the KioskNet System (Extended Version),''} 
\emph{University of Waterloo Technical Report, November 2007.}
%\item \emph{Hossein Falaki} and Rajat Sethi, {\bf ''Energy Modeling for KioskNet,''} \emph{ACM MobiCom Workshop on Challenged Networks (Poster Session).}

\item S. Guo, \emph{M.H. Falaki}, E.A. Oliver, S. Ur Rahman, A. Seth,
M.A. Zaharia, and S. Keshav, 
{\bf ``Very Low-Cost Internet Access Using KioskNet,''}
\emph{ACM CCR, October 2007.}

\item Earl Oliver and \emph{Hossein Falaki}, 
{\bf ``Performance Evaluation and Analysis of Delay Tolerant Networking,''} 
\emph{ACM MobiEval, June 2007.}

\item Alireza Vahdatpour, Ahmadreza Tavakoli and \emph{Hossein Falaki},
{\bf ``Hierarchical Graph: A New Cost Effective Architecture for Network on Chip,''}
\emph{IFIP EUC, December 2005.}
\end{itemize}

\end{resume}
\end{document}

